%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Structured General Purpose Assignment
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Ted Pavlic (http://www.tedpavlic.com)
%
% Note:
% The \lipsum[#] commands throughout this template generate dummy text
% to fill the template out. These commands should all be removed when
% writing assignment content.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}

\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{multirow}

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.5} % Line spacing

% Set up the header and footer
\pagestyle{fancy}
\lhead{\hmwkAuthorName} % Top left header
\chead{\hmwkClass\ (\hmwkTitle)} % Top center header
%%\rhead{\firstxmark}
\rhead{} % Top right header
\lfoot{\lastxmark} % Bottom left footer
\cfoot{} % Bottom center footer
\rfoot{Page\ \thepage\ of\ \pageref{LastPage}} % Bottom right footer
\renewcommand\headrulewidth{0.4pt} % Size of the header rule
\renewcommand\footrulewidth{0.4pt} % Size of the footer rule

\setlength\parindent{0pt} % Removes all indentation from paragraphs

%----------------------------------------------------------------------------------------
%	DOCUMENT STRUCTURE COMMANDS
%	Skip this unless you know what you're doing
%----------------------------------------------------------------------------------------

% Header and footer for when a page split occurs within a problem environment
\newcommand{\enterProblemHeader}[1]{
\nobreak\extramarks{#1}{#1 continued on next page\ldots}\nobreak
\nobreak\extramarks{#1 (continued)}{#1 continued on next page\ldots}\nobreak
}

% Header and footer for when a page split occurs between problem environments
\newcommand{\exitProblemHeader}[1]{
\nobreak\extramarks{#1 (continued)}{#1 continued on next page\ldots}\nobreak
\nobreak\extramarks{#1}{}\nobreak
}

\setcounter{secnumdepth}{0} % Removes default section numbers
\newcounter{homeworkProblemCounter} % Creates a counter to keep track of the number of problems

\newcommand{\homeworkProblemName}{}
\newenvironment{homeworkProblem}[1][Question \arabic{homeworkProblemCounter}]{ % Makes a new environment called homeworkProblem which takes 1 argument (custom name) but the default is "Question #"
\stepcounter{homeworkProblemCounter} % Increase counter for number of problems
\renewcommand{\homeworkProblemName}{#1} % Assign \homeworkProblemName the name of the problem
\section{\homeworkProblemName} % Make a section in the document with the custom problem count
\enterProblemHeader{\homeworkProblemName} % Header and footer within the environment
}{
\exitProblemHeader{\homeworkProblemName} % Header and footer after the environment
}

\newcommand{\problemAnswer}[1]{ % Defines the problem answer command with the content as the only argument
\noindent\framebox[\columnwidth][c]{\begin{minipage}{0.98\columnwidth}#1\end{minipage}} % Makes the box around the problem answer and puts the content inside
}

\newcommand{\homeworkSectionName}{}
\newenvironment{homeworkSection}[1]{ % New environment for sections within homework problems, takes 1 argument - the name of the section
\renewcommand{\homeworkSectionName}{#1} % Assign \homeworkSectionName to the name of the section from the environment argument
\subsection{\homeworkSectionName} % Make a subsection with the custom name of the subsection
\enterProblemHeader{\homeworkProblemName\ [\homeworkSectionName]} % Header and footer within the environment
}{
\enterProblemHeader{\homeworkProblemName} % Header and footer after the environment
}

%----------------------------------------------------------------------------------------
%	EXPECTATION AND VARIANCE OPERATOR
%----------------------------------------------------------------------------------------
 \newcommand{\E}{\mathrm{E}}
 \newcommand{\Var}{\mathrm{Var}}
 \newcommand{\Cov}{\mathrm{Cov}}
 \newcommand{\Corr}{\mathrm{Corr}}

%----------------------------------------------------------------------------------------
%	NAME AND CLASS SECTION
%----------------------------------------------------------------------------------------

\newcommand{\hmwkTitle}{Problem Set\ \#4} % Assignment title
\newcommand{\hmwkDueDate}{Sunday,\ May\ 6,\ 2018} % Due date
\newcommand{\hmwkClass}{FIN\ 521} % Course/class
\newcommand{\hmwkClassTime}{2:00pm} % Class/lecture time
\newcommand{\hmwkAuthorName}{Wanbae Park} % Your name

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title{
\vspace{2in}
\textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
\normalsize\vspace{0.1in}\small{Due\ on\ \hmwkDueDate}\\
\vspace{3in}
}

\author{\textbf{\hmwkAuthorName}}
\date{} % Insert date here if you want it to appear below your name

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle

%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS
%----------------------------------------------------------------------------------------

%\setcounter{tocdepth}{1} % Uncomment this line if you don't want subsections listed in the ToC

%%\newpage
%%\tableofcontents
\newpage

%----------------------------------------------------------------------------------------
%	QUESTION 1
%----------------------------------------------------------------------------------------
\begin{homeworkProblem}
    \begin{enumerate}[a.]
        \item   %% a.
        Let $x$ denote the current price per share. Then market capitalization
        of the firm is equal to $x \times$ 8 million dollars before the investment.
        After investment, market capitalization of the firm will be $8x + 1$
        million dollars, and the portion of venture capitalist will be
        $\frac{1}{8x + 1}$, which will be equal to 0.2.
        Therefore, by solving the equation, current price of share is equal to
        0.5 dollars, and the venture capitalist will get 2 million shares.
        \item   %% b.
        Since there are 10 million shares after investment and price per share
        is \$0.5, the value of firm is equal to $0.5 \times 2 = 1$ million dollars.
    \end{enumerate}
\end{homeworkProblem}

%----------------------------------------------------------------------------------------
%	QUESTION 2
%----------------------------------------------------------------------------------------
\begin{homeworkProblem}
    \begin{enumerate}[a.]
        \item   %% a.
        Since the IPO price was \$20 per share and there is 7\% underwriting
        spread, the amount of capital raise is equal to
        $(1 - 0.07) \times 20 \times 5 = 93$ million dollars.
        \item   %% b.
        After IPO, since 5 million shares are added, there are 15 million shares
        of the firm. Because the share price increased to \$50, market value of
        equity of the firm is equal to $50 \times 15 = 750$ million dollars.
        \item   %% c.
        Since market is perfect, the current share price of firm must be equal
        to \$50. Therefore, because there is 10 million shares before issuing
        stock, pre-money value of the equity is equal to $50 \times 10 = 500$
        million dollars. Under perfect market, because the firm will issue stock
        at the fair price: \$50, if the firm issues 5 million shares, the amount
        of capital risen is equal to $50 \times 5 = 250$ million dollars.
        Therefore, post-money value of equity is equal to 750 million dollars.
        Under this circumstances, in order to raise 93 million dollars as in
        question a, it needs to issue $93 / 50 = 1.86$ million shares, which
        is quite less than the amount of issuance at question a.
        \item   %% d.
        Due to underpricing and underwriting spread, the firm can only raise
        93 million dollars for issuing 5 million shares, comparing 250 million
        dollars when market is perfect. Therefore, it can be concluded that
        $250 - 93 = 157$ million dollars are left on the table due to market
        imperfection.
    \end{enumerate}
\end{homeworkProblem}

%----------------------------------------------------------------------------------------
%	QUESTION 3
%----------------------------------------------------------------------------------------
\begin{homeworkProblem}
    \begin{enumerate}[a.]
        \item   %% a.
        Since the amount of money risen only depends on primary shares.
        Therefore, because the amount of primary share is equal to 5 million,
        considering the underwriter charges, the amount of money risen is
        equal to $5 \times 42.50 \times (1 - 0.05) = 201.875$ million dollars.
        \item   %% b.
        Since the venture capitalist sold 3 million shares, they received
        $3 \times 42.50 \times (1 - 0.05) = 121.125$ million dollars.
    \end{enumerate}
\end{homeworkProblem}

%----------------------------------------------------------------------------------------
%	QUESTION 4
%----------------------------------------------------------------------------------------
\begin{homeworkProblem}
    \begin{enumerate}[a.]
        \item   %% a.
        From the question, the total earning of my company and TargetCo is
        4 million and 2 million dollars respectively.
        Since the market value of equity of TargetCo is 2.5 million dollars,
        in order to buy TargetCo, my company has to issue $25,000,000 / 40
        = 625,000$ shares, if there is no premium. Therefore, since the number
        of shares increases to 1,625,000 and total earning becomes 6 million
        dollars, EPS will be $6,000,000 / 1,625,000 = \$3.69$.
        \item   %% b.
        Since there is 20\% premium to buy TargetCo, shareholders of TargetCo
        will get $\frac{25,000,000}{40} \times 1.2 = 750,000$ shares of my
        company. Since the total earning of mergered firm is 6 million dollars,
        EPS will be equal to $6,000,000 / 1,750,000 = \$3.43$.
        \item   %% c.
        Earning per share in (b) is less than (a) because there is a premium
        in merger, and the amount of premium is financed by issuing stock.
        Since there is no synergy, the original shareholders of my firm will
        be worse off because they paid premium. In contrast, shareholders of
        TargetCo will be better of because they get premium.
        \item   %% d.
        Before the merger, P/E ratio of my company is $40 / 4 = 10$.
        However, after the merger, because there is no synergy, P/E ratio
        will be increased to $40 / 3.69 = 10.33$. TargetCo's P/E ratio
        before the merger is $25 / 2 = 12.5$. By merging firm which has higher
        EPS, a company can raise its P/E ratio although there is no fundamental
        effect.
    \end{enumerate}
\end{homeworkProblem}

%----------------------------------------------------------------------------------------
%	QUESTION 5
%----------------------------------------------------------------------------------------
\begin{homeworkProblem}
    The maximum exchange ratio is attained when NPV of merger is zero.
    This condition pins down to the following equation.
    \begin{equation*}
        Exchange~Ratio = \frac{P_T}{P_A}\left( 1 + \frac{S}{T} \right)
    \end{equation*}
    where $P_T$ and $P_A$ is share price of target firm and the original firm,
    respectively. $S$ and $T$ denote the value of synergy and target firm.
    Therefore, plugging the given value to the equation above, we can find that
    the maximum exchange ratio as $\frac{25}{35}(1 + \frac{1}{4}) = 0.893$.
\end{homeworkProblem}

%----------------------------------------------------------------------------------------
%	QUESTION 6
%----------------------------------------------------------------------------------------
\begin{homeworkProblem}
    \begin{enumerate}[a.]
        \item   %% a.
        In this case, since there are cash flows only at 2 dates
        (investment date and end of 10 years), the IRR can be calculated by
        solving the following equation.
        \begin{equation*}
            80 = \frac{400}{(1 + IRR)^{10}}
        \end{equation*}
        By solving the equation above, the IRR is calculated as 17.46\%.
        \item   %% b.
        In this case, there are 4 sources of cash flow. First, the amount of
        initial investment is 100 million dollars. Second, the limited partner
        should pay 2 million dollars at each year for management fee.
        Third, the investment will be worth 400 million dollars.
        Fourth, because the net profit of the fund is $400 - 100 - 2 \times 10
        = 280$, the limited partner shoula pay $280 \times 0.2 = 56$ million
        dollars for interest. Considering the cash flows, IRR is calculated
        as 11.94\%.
    \end{enumerate}
\end{homeworkProblem}

%----------------------------------------------------------------------------------------
%	QUESTION 7
%----------------------------------------------------------------------------------------
\begin{homeworkProblem}
    There are lots of ways to motivate managers to act for owner's interest.
    First, paying for their performance can be a way like granting executive
    stock options. Second, monitoring by board of directors and other monitors
    can reduce agency costs. Third, shareholders may try to replace directors
    in board election. Fourth, by executing hostile takeover, it is possible to
    reduce agency cost.
\end{homeworkProblem}

%----------------------------------------------------------------------------------------
%	QUESTION 8
%----------------------------------------------------------------------------------------
\begin{homeworkProblem}
    Since the CEO has 3\% of the firm, if the acquisition is executed,
    CEO will lose $0.03 \times 50 = 1.5$ million dollars. However, since present
    value of compensation is 5 million dollars. By acquiring, CEO can get
    3.5 million dollars, which is profit to CEO. However, since the acquisition
    destroys 50 million of GreenFrame's value, shareholders will be worse off
    unless present value of synergy is larger than 50 million dollars.
\end{homeworkProblem}

\end{document}
